Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-03-26 SupportingInformation.Rmd
modified r chunk for asym sens results with b=+-0.1, +-0.5

}
#----------------------------------------------------------
N<-5000
r<-0.8
a<-0.2
numkeep_last<-500
temp<-get_noise_glob_loc_mat(N=N,r=r)
mg<-temp$mg
ml<-temp$ml

resloc<-"./Results/asym_sens_results/"
ans_b_0.1<-plotter_asym_sens_b_varn(mg=mg,ml=ml,a=a,b=0.1,numkeep_last=numkeep_last,ploton=T,resloc=resloc)
ans_b_neg0.1<-plotter_asym_sens_b_varn(mg=mg,ml=ml,a=a,b=-0.1,numkeep_last=numkeep_last,ploton=T,resloc=resloc)
ans_b_0.9<-plotter_asym_sens_b_varn(mg=mg,ml=ml,a=a,b=0.9,numkeep_last=numkeep_last,ploton=T,resloc=resloc)
ans_b_neg0.9<-plotter_asym_sens_b_varn(mg=mg,ml=ml,a=a,b=-0.9,numkeep_last=numkeep_last,ploton=T,resloc=resloc)

vlist_b_0.1_b_0.9<-c(ans_b_0.1,ans_b_neg0.1,ans_b_0.9,ans_b_neg0.9) # a list of 8 matrices

summary_stat<-as.data.frame(matrix(NA,7,8),stringsAsFactors = F) # Table for model selection summary
rownames(summary_stat)<-c("bestcop_AICw","N_AICw","relLTdep_AICw","relUTdep_AICw","p_CvM","p_KS","BS_success%")
#bg <- intToUtf8(0x03B2) 
cnm<-c("b_0.1_g~1~","b_0.1_g~2~","b_-0.1_g~1~","b_-0.1_g~2~","b_0.9_g~1~","b_0.9_g~2~","b_-0.9_g~1~","b_-0.9_g~2~")
#cname<-paste0(bg,cnm)
colnames(summary_stat)<-cnm

ms_asym_b_0.1_b_0.9<-vector(mode = "list", length = 8) # initializing list to store model selection results for all possible b variation
names(ms_asym_b_0.1_b_0.9)<-cnm

stat_npa_asym_b_0.1_b_0.9<-vector(mode = "list", length = 8) # initializing list to store NPA results for all possible b variation
names(stat_npa_asym_b_0.1_b_0.9)<-cnm

for(ic in c(1:8)){
  v<-vlist_b_0.1_b_0.9[[ic]]
  res<-OurBiCopSelect(u1=v[,1],u2=v[,2],families=c(1,3:10,13:14,16:20),level=0.05,
                      AICBIC="AIC",numBSsmall=100,pthresh=0.2,numBSlarge=1000,
                      gofnormal=F,status=F)

  ms_asym_b_0.1_b_0.9[[ic]]<-res

@@

  stat_npa_asym_b_0.1_b_0.9[[ic]]<-bivfunctionplot(v=v,resloc="./Results/asym_sens_results/",nametag=cnm[ic],numbin=10)

@@

saveRDS(summary_stat,"./Results/asym_sens_results/b_variation_summary_stat.RDS")
saveRDS(ms_asym_b_0.1_b_0.9,"./Results/asym_sens_results/ms_asym_b_0.1_b_0.9.RDS")
saveRDS(stat_npa_asym_b_0.1_b_0.9,"./Results/asym_sens_results/stat_npa_asym_b_0.1_b_0.9.RDS")
```

```{r overwritting_plots_asym_cop,echo=F,results="hide"}
pdf("./Results/asym_sens_results/a_0.2_b_0.1_r_0.8_asym_sens.pdf",height=3,width=6)
op<-par(mfrow=c(1,2),mar=c(3.5,4,1,1),mgp=c(2.2,0.5,0))
pop<-ans_b_0.1$pop
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,cex.axis=1,col="grey",pch=20,cex=0.6)
text(0.1,0.95,"A",cex=2)
pop<-ans_b_0.1$pop_d
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,cex.axis=1,col="grey",pch=20,cex=0.6)
text(0.1,0.95,"B",cex=2)
par(op)
dev.off()

pdf("./Results/asym_sens_results/a_0.2_b_-0.1_r_0.8_asym_sens.pdf",height=3,width=6)
op<-par(mfrow=c(1,2),mar=c(3.5,4,1,1),mgp=c(2.2,0.5,0))
pop<-ans_b_neg0.1$pop
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,cex.axis=1,col="grey",pch=20,cex=0.6)
text(0.1,0.95,"A",cex=2)
pop<-ans_b_neg0.1$pop_d
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,cex.axis=1,col="grey",pch=20,cex=0.6)
text(0.1,0.95,"B",cex=2)
par(op)
dev.off()

pdf("./Results/asym_sens_results/a_0.2_b_0.9_r_0.8_asym_sens.pdf",height=3,width=6)
op<-par(mfrow=c(1,2),mar=c(3.5,4,1,1),mgp=c(2.2,0.5,0))
pop<-ans_b_0.9$pop
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,cex.axis=1,col="grey",pch=20,cex=0.6)
text(0.1,0.95,"A",cex=2)
pop<-ans_b_0.9$pop_d
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,cex.axis=1,col="grey",pch=20,cex=0.6)
text(0.1,0.95,"B",cex=2)
par(op)
dev.off()

pdf("./Results/asym_sens_results/a_0.2_b_-0.9_r_0.8_asym_sens.pdf",height=3,width=6)
op<-par(mfrow=c(1,2),mar=c(3.5,4,1,1),mgp=c(2.2,0.5,0))
pop<-ans_b_neg0.9$pop
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,cex.axis=1,col="grey",pch=20,cex=0.6)
text(0.1,0.95,"A",cex=2)
pop<-ans_b_neg0.9$pop_d
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,cex.axis=1,col="grey",pch=20,cex=0.6)
text(0.1,0.95,"B",cex=2)
par(op)
dev.off()
```

```{r tab_summary_stat_asym_sens,echo=F,results="markup"}
summary_stat<-summary_stat[c(1:6),]
rownames(summary_stat)<-c("Best-fit copula AICw","N-copula AICw","Model-avg. LT","Model-avg. UT","p, CvM","p, KS")
knitr::kable(summary_stat, booktabs = T, escape=F,
             format = "latex", linesep = "",
             digits=3, col.names=c("b=0.1, g$_{1}$","b=0.1, g$_{2}$",
                                   "b=-0.1, g$_{1}$","b=-0.1, g$_{2}$",
                                   "b=0.9, g$_{1}$","b=0.9, g$_{2}$",
                                   "b=-0.9, g$_{1}$","b=-0.9, g$_{2}$"),
      caption.short="Asymmetric sensitivity model, model selection results",
      caption="Asymmetric sensitivity model, model selection results. 
The output of simulations from the second model detailed in 
the methods section for Q2 (i.e., Figs \\ref{MT-fig_ms_asym_b_0.1} and 
\\ref{fig_ms_asym_b_-0.1}-\\ref{fig_ms_asym_b_-0.9}) were subjected to the model 
selection procedures detailed in the 
methods section for Q1. Best-fit copula AICw: the AIC weight of the best-fitting copula family;
N-copula AICw: the AIC weight of the N copula family; Model-avg. LT: the lower-tail 
statistic, weighted-averaged across models using AICw; Model-avg. UT: same, but for the 
upper-tail statistic; p, CvM: p-value for goodness of fit test of the best-fitting copula
family using the test based on the Cramer-von Mises statistic; p, KS: p-value for goodness of fit 
test of the best-fitting copula family using the test based on the Kolmogorov-Smirnov 
statistic.\\label{tab_summary_stat_asym_sens}")
```

@@

tab_asym<-readRDS("./Results/asym_sens_results/stat_npa_asym_b_0.1_b_0.9.RDS")
tab_stat_npa_asym<-c()
for(i in c(1:8)){
  temp<-make_table_stat_fn(data=tab_asym[[i]])
  tab_stat_npa_asym<-rbind(tab_stat_npa_asym,temp)
}
gtext<-c("b=0.1, g$_{1}$","b=0.1, g$_{2}$","b=-0.1, g$_{1}$","b=-0.1, g$_{2}$","b=0.9, g$_{1}$","b=0.9, g$_{2}$","b=-0.9, g$_{1}$","b=-0.9, g$_{2}$")
tab_stat_npa_asym<-cbind(b=rep(c(0.1,0.1,-0.1,-0.1,0.9,0.9,-0.9,-0.9),each=3),
  g=rep(c("g$_{1}$","g$_{2}$","g$_{1}$","g$_{2}$","g$_{1}$","g$_{2}$","g$_{1}$","g$_{2}$"),each=3),tab_stat_npa_asym)
knitr::kable(tab_stat_npa_asym, booktabs = T, longtable=T,
             format = "latex",linesep = "",escape=F,
             caption.short = "Asymmetric sensitivity model, nonparametric statistics results",
             caption ="Asymmetric sensitivity model, nonparametric statistics results. 
The output of simulations from the second model detailed in 
the methods section for Q2 (i.e., Figs \\ref{MT-fig_ms_asym_b_0.1} and 
\\ref{fig_ms_asym_b_-0.1}-\\ref{fig_ms_asym_b_-0.9}) were subjected to nonparamtric statistical 
analyses decribed in the methods section for Q1. The listed statistic was computed for the
output of the model with the indicated b and g, and the value was compared to 1000 values
of the same statistic computed on surrogate time series randomized to have N-copula structure
(see methods for Q1). A table entry $<X$ (respectively, $>X$) indicates the value of the 
given statistic on the data was less (respectively, more) than its value on $X$ of the 
surrogates, so entries of the form $<X$ (respectively, $>X$) for $X$ equal to $975$ or above 
indicate that upper-tail (respectively, lower-tail) dependence was significantly stronger than 
lower-tail dependence compared to an N-copula null hypothesis. `FS' stands for `first slice'
and refers to the bounds 0 to 0.1; `LS' stands for `last slice' and refers to the bounds
0.9 to 1.\\label{tab_stat_npa_asym}")#%>%
 #            kable_styling()%>%
 #            group_rows(index=setNames(c(3,3,3,3,3,3,3,3), gtext))
 #            group_rows("b=0.1, g$_{1}$", 2,4, escape=F) %>%
 #            group_rows("b=0.1, g$_{2}$", 5,7, escape=F) %>%
 #            group_rows("b=-0.1, g$_{1}$", 8,10, escape=F) %>%
 #            group_rows("b=-0.1, g$_{2}$", 11,13, escape=F) %>%
 #            group_rows("b=0.9, g$_{1}$", 14,16, escape=F) %>%
 #            group_rows("b=0.9, g$_{2}$", 17,19, escape=F) %>%
 #            group_rows("b=-0.9, g$_{1}$", 20,22, escape=F) %>%
 #            group_rows("b=-0.9, g$_{2}$", 23,25, escape=F)
```

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/asym_sens_results/a_0.2_b_0.9_r_0.8_asym_sens.pdf}
\caption{Analogous to Fig. \ref{MT-fig_ms_asym_b_0.1}, but using $b=0.9$.\label{fig_ms_asym_b_0.9}}
\end{center}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/asym_sens_results/a_0.2_b_-0.9_r_0.8_asym_sens.pdf}
\caption{Analogous to Fig. \ref{MT-fig_ms_asym_b_0.1}, but using $b=-0.9$.\label{fig_ms_asym_b_-0.9}}
\end{center}
\end{figure}

>>>>

}
#----------------------------------------------------------
N<-25000
r<-0.8
a<-0.2
numkeep_last<-2500
temp<-get_noise_glob_loc_mat(N=N,r=r)
mg<-temp$mg
ml<-temp$ml

resloc<-"./Results/asym_sens_results/"
ans_b_0.1<-plotter_asym_sens_b_varn(mg=mg,ml=ml,a=a,b=0.1,numkeep_last=numkeep_last,ploton=T,resloc=resloc)
ans_b_neg0.1<-plotter_asym_sens_b_varn(mg=mg,ml=ml,a=a,b=-0.1,numkeep_last=numkeep_last,ploton=T,resloc=resloc)
ans_b_0.5<-plotter_asym_sens_b_varn(mg=mg,ml=ml,a=a,b=0.5,numkeep_last=numkeep_last,ploton=T,resloc=resloc)
ans_b_neg0.5<-plotter_asym_sens_b_varn(mg=mg,ml=ml,a=a,b=-0.5,numkeep_last=numkeep_last,ploton=T,resloc=resloc)

vlist_b_0.1_b_0.5<-c(ans_b_0.1,ans_b_neg0.1,ans_b_0.5,ans_b_neg0.5) # a list of 8 matrices

summary_stat<-as.data.frame(matrix(NA,7,8),stringsAsFactors = F) # Table for model selection summary
rownames(summary_stat)<-c("bestcop_AICw","N_AICw","relLTdep_AICw","relUTdep_AICw","p_CvM","p_KS","BS_success%")
#bg <- intToUtf8(0x03B2) 
cnm<-c("b_0.1_g~1~","b_0.1_g~2~","b_-0.1_g~1~","b_-0.1_g~2~","b_0.5_g~1~","b_0.5_g~2~","b_-0.5_g~1~","b_-0.5_g~2~")
#cname<-paste0(bg,cnm)
colnames(summary_stat)<-cnm

ms_asym_b_0.1_b_0.5<-vector(mode = "list", length = 8) # initializing list to store model selection results for all possible b variation
names(ms_asym_b_0.1_b_0.5)<-cnm

stat_npa_asym_b_0.1_b_0.5<-vector(mode = "list", length = 8) # initializing list to store NPA results for all possible b variation
names(stat_npa_asym_b_0.1_b_0.5)<-cnm

for(ic in c(1:8)){
  v<-vlist_b_0.1_b_0.5[[ic]]
  res<-OurBiCopSelect(u1=v[,1],u2=v[,2],families=c(1,3:10,13:14,16:20),level=0.05,
                      AICBIC="AIC",numBSsmall=100,pthresh=0.2,numBSlarge=1000,
                      gofnormal=F,status=F)

  ms_asym_b_0.1_b_0.5[[ic]]<-res

@@

  stat_npa_asym_b_0.1_b_0.5[[ic]]<-bivfunctionplot(v=v,resloc="./Results/asym_sens_results/",nametag=cnm[ic],numbin=10)

@@

saveRDS(summary_stat,"./Results/asym_sens_results/b_variation_summary_stat.RDS")
saveRDS(ms_asym_b_0.1_b_0.5,"./Results/asym_sens_results/ms_asym_b_0.1_b_0.5.RDS")
saveRDS(stat_npa_asym_b_0.1_b_0.5,"./Results/asym_sens_results/stat_npa_asym_b_0.1_b_0.5.RDS")
```

```{r overwritting_plots_asym_cop,echo=F,results="hide"}
pdf("./Results/asym_sens_results/a_0.2_b_0.1_r_0.8_asym_sens.pdf",height=3,width=6)
op<-par(mfrow=c(1,2),mar=c(3.5,4,1,1),mgp=c(2.2,0.5,0))
pop<-ans_b_0.1$pop
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,
     cex.axis=1,col=rgb(0,0,0,0.5),pch=20,cex=0.6)
text(0.1,0.95,"A",cex=2)
pop<-ans_b_0.1$pop_d
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,
     cex.axis=1,pch=20,col=rgb(0,0,0,0.5),cex=0.6)
text(0.1,0.95,"B",cex=2)
par(op)
dev.off()

pdf("./Results/asym_sens_results/a_0.2_b_-0.1_r_0.8_asym_sens.pdf",height=3,width=6)
op<-par(mfrow=c(1,2),mar=c(3.5,4,1,1),mgp=c(2.2,0.5,0))
pop<-ans_b_neg0.1$pop
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,
     cex.axis=1,pch=20,col=rgb(0,0,0,0.5),cex=0.6)
text(0.1,0.95,"A",cex=2)
pop<-ans_b_neg0.1$pop_d
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,
     cex.axis=1,col=rgb(0,0,0,0.5),pch=20,cex=0.6)
text(0.1,0.95,"B",cex=2)
par(op)
dev.off()

pdf("./Results/asym_sens_results/a_0.2_b_0.5_r_0.8_asym_sens.pdf",height=3,width=6)
op<-par(mfrow=c(1,2),mar=c(3.5,4,1,1),mgp=c(2.2,0.5,0))
pop<-ans_b_0.5$pop
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,
     cex.axis=1,col=rgb(0,0,0,0.5),pch=20,cex=0.6)
text(0.1,0.95,"A",cex=2)
pop<-ans_b_0.5$pop_d
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,
     cex.axis=1,col=rgb(0,0,0,0.5),pch=20,cex=0.6)
text(0.1,0.95,"B",cex=2)
par(op)
dev.off()

pdf("./Results/asym_sens_results/a_0.2_b_-0.5_r_0.8_asym_sens.pdf",height=3,width=6)
op<-par(mfrow=c(1,2),mar=c(3.5,4,1,1),mgp=c(2.2,0.5,0))
pop<-ans_b_neg0.5$pop
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,
     cex.axis=1,col=rgb(0,0,0,0.5),pch=20,cex=0.6)
text(0.1,0.95,"A",cex=2)
pop<-ans_b_neg0.5$pop_d
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,
     cex.axis=1,col=rgb(0,0,0,0.5),pch=20,cex=0.6)
text(0.1,0.95,"B",cex=2)
par(op)
dev.off()
```

```{r tab_summary_stat_asym_sens,echo=F,results="markup"}
summary_stat<-summary_stat[c(1:6),]
rownames(summary_stat)<-c("Best-fit copula AICw","N-copula AICw","Model-avg. LT","Model-avg. UT","p, CvM","p, KS")
knitr::kable(summary_stat, booktabs = T, escape=F,
             format = "latex", linesep = "",
             digits=4, col.names=c("b=0.1, g$_{1}$","b=0.1, g$_{2}$",
                                   "b=-0.1, g$_{1}$","b=-0.1, g$_{2}$",
                                   "b=0.5, g$_{1}$","b=0.5, g$_{2}$",
                                   "b=-0.5, g$_{1}$","b=-0.5, g$_{2}$"),
      caption.short="Asymmetric sensitivity model, model selection results",
      caption="Asymmetric sensitivity model, model selection results. 
The output of simulations from the second model detailed in 
the methods section for Q2 (i.e., Figs \\ref{MT-fig_ms_asym_b_0.1} and 
\\ref{fig_ms_asym_b_-0.1}-\\ref{fig_ms_asym_b_-0.5}) were subjected to the model 
selection procedures detailed in the 
methods section for Q1. Best-fit copula AICw: the AIC weight of the best-fitting copula family;
N-copula AICw: the AIC weight of the N copula family; Model-avg. LT: the lower-tail 
statistic, weighted-averaged across models using AICw; Model-avg. UT: same, but for the 
upper-tail statistic; p, CvM: p-value for goodness of fit test of the best-fitting copula
family using the test based on the Cramer-von Mises statistic; p, KS: p-value for goodness of fit 
test of the best-fitting copula family using the test based on the Kolmogorov-Smirnov 
statistic.\\label{tab_summary_stat_asym_sens}")
```

@@

tab_asym<-readRDS("./Results/asym_sens_results/stat_npa_asym_b_0.1_b_0.5.RDS")
tab_stat_npa_asym<-c()
for(i in c(1:8)){
  temp<-make_table_stat_fn(data=tab_asym[[i]])
  tab_stat_npa_asym<-rbind(tab_stat_npa_asym,temp)
}
gtext<-c("b=0.1, g$_{1}$","b=0.1, g$_{2}$","b=-0.1, g$_{1}$","b=-0.1, g$_{2}$","b=0.5, g$_{1}$","b=0.5, g$_{2}$","b=-0.5, g$_{1}$","b=-0.5, g$_{2}$")
tab_stat_npa_asym<-cbind(b=rep(c(0.1,0.1,-0.1,-0.1,0.5,0.5,-0.5,-0.5),each=3),
  g=rep(c("g$_{1}$","g$_{2}$","g$_{1}$","g$_{2}$","g$_{1}$","g$_{2}$","g$_{1}$","g$_{2}$"),each=3),tab_stat_npa_asym)
knitr::kable(tab_stat_npa_asym, booktabs = T, longtable=T,
             format = "latex",linesep = "",escape=F,
             caption.short = "Asymmetric sensitivity model, nonparametric statistics results",
             caption ="Asymmetric sensitivity model, nonparametric statistics results. 
The output of simulations from the second model detailed in 
the methods section for Q2 (i.e., Figs \\ref{MT-fig_ms_asym_b_0.1} and 
\\ref{fig_ms_asym_b_-0.1}-\\ref{fig_ms_asym_b_-0.5}) were subjected to nonparamtric statistical 
analyses decribed in the methods section for Q1. The listed statistic was computed for the
output of the model with the indicated b and g, and the value was compared to 1000 values
of the same statistic computed on surrogate time series randomized to have N-copula structure
(see methods for Q1). A table entry $<X$ (respectively, $>X$) indicates the value of the 
given statistic on the data was less (respectively, more) than its value on $X$ of the 
surrogates, so entries of the form $<X$ (respectively, $>X$) for $X$ equal to $975$ or above 
indicate that upper-tail (respectively, lower-tail) dependence was significantly stronger than 
lower-tail dependence compared to an N-copula null hypothesis. `FS' stands for `first slice'
and refers to the bounds 0 to 0.1; `LS' stands for `last slice' and refers to the bounds
0.9 to 1.\\label{tab_stat_npa_asym}")#%>%
 #            kable_styling()%>%
 #            group_rows(index=setNames(c(3,3,3,3,3,3,3,3), gtext))
 #            group_rows("b=0.1, g$_{1}$", 2,4, escape=F) %>%
 #            group_rows("b=0.1, g$_{2}$", 5,7, escape=F) %>%
 #            group_rows("b=-0.1, g$_{1}$", 8,10, escape=F) %>%
 #            group_rows("b=-0.1, g$_{2}$", 11,13, escape=F) %>%
 #            group_rows("b=0.9, g$_{1}$", 14,16, escape=F) %>%
 #            group_rows("b=0.9, g$_{2}$", 17,19, escape=F) %>%
 #            group_rows("b=-0.9, g$_{1}$", 20,22, escape=F) %>%
 #            group_rows("b=-0.9, g$_{2}$", 23,25, escape=F)
```

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/asym_sens_results/a_0.2_b_0.5_r_0.8_asym_sens.pdf}
\caption{Analogous to Fig. \ref{MT-fig_ms_asym_b_0.1}, but using $b=0.9$.\label{fig_ms_asym_b_0.5}}
\end{center}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/asym_sens_results/a_0.2_b_-0.5_r_0.8_asym_sens.pdf}
\caption{Analogous to Fig. \ref{MT-fig_ms_asym_b_0.1}, but using $b=-0.9$.\label{fig_ms_asym_b_-0.5}}
\end{center}
\end{figure}
